Why there are more species in several small patches vs few large patches:

### 2024-10-25 ms_SLOSS_title.Rmd
Update PLS

---
title: "Why there are more species in several small patches vs few large patches:
  a multi-species modeling approach"
bibliography: sloss_bib.bib
csl: "ecology-letters.csl"

output:
  pdf_document: 
    includes:
      in_header: margins.sty
---

>>>>

---
title: "Why there are more species in several small patches vs few large patches:
  a multi-species modeling approach"
bibliography: sloss_bib.bib
csl: "ecology-letters.csl"
output:
  word_document: default
  pdf_document:
    includes:
      in_header: margins.sty
---
